% !TEX TS-program = xelatex
% !TEX encoding = UTF-8

% \documentclass[a4paper,10pt,oneside]{article}
\documentclass[letterpaper,10pt,oneside]{simpleresumecv}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Devin Lehmacher}
\newcommand{\CVTitle}{Devin Lehmacher's Resume for Apple}
\newcommand{\CVNote}{Resume compiled on {\today} for Apple}
\newcommand{\CVWebpage}{github.com/lehmacdj}

% PDF settings and properties.
\hypersetup{%
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
pdfpagemode={},
bookmarks=true,
unicode=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\title{\CVAuthor}

\begin{subtitle}
\href{https://www.google.com/maps/place/232+Kings+Way,+Clemson,+SC+29631,+USA}
{232 Kings Way, Clemson, SC 29631, USA}
\par
\href{mailto:djl329@cornell.edu}
{djl329@cornell.edu}
\,\SubBulletSymbol\,
+1\,(864)\,722-3014
\,\SubBulletSymbol\,
\href{https://\CVWebpage}
{\CVWebpage}
\end{subtitle}

\begin{body}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\section%
{Education}
{Education}
{PDF:Education}

\href{https://www.cornell.edu}
{\textbf{Cornell University}},
Ithaca, NY 14853
\hfill
\DatestampYMD{2015}{08}{25} --
Present
\GapNoBreak%
\BulletItem%
Bachelors of Arts, degree anticipated
\DatestampYM{2019}{05}
\begin{detail}
\SubBulletItem%
Majors:
\href{https://www.cs.cornell.edu}
{Computer Science}
and
\href{https://www.biology.cornell.edu}
{Biology}
\SubBulletItem%
Cumulative GPA:\@ 3.39
\end{detail}

%%%%%%%%%%%%%%%%%%%%%%%%%
%% RESEARCH EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\section%
{Research Experience}
{Research Experience}
{PDF:ResearchExperience}

\href{https://www.clemson.edu}
{\textbf{Clemson University}},
College of Science

\GapNoBreak%
\hfill
\DatestampYMD{2015}{06}{15} --
Present
\BulletItem%
Undergraduate Research Student, Physics and Astronomy
\begin{detail}
\SubBulletItem%
Project:
MedusaLoop: Protein Loop Modeling Server
\SubBulletItem%
Supervisors:
Dr.\ Feng Ding
\SubBulletItem%
Research areas:
Protein loops, web development, linux, shell scripting
\end{detail}

\section%
{Campus Activities}
{Campus Activities}
{PDF:CampusActivities}

{\textbf{Cornell Quidditch}},
Cornell University
\hfill
\DatestampYMD{2015}{09}{05} --
Present

\GapNoBreak%
\BulletItem%
Captain

{\textbf{Shake Ultimate}},
Cornell University
\hfill
\DatestampYMD{2015}{09}{08} --
Present

\GapNoBreak%
\BulletItem%
Cornell's Ultimate Frisbee B-Team.

{\textbf{Cornell Mafia Club}},
Cornell University
\hfill
\DatestampYMD{2015}{10}{23} --
Present

\GapNoBreak%
\BulletItem%
Play mafia a game about logical deduction and analysis of other players.

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% OTHER WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section%
{Other Work\newline
Experience}
{Other Work Experience}
{PDF:OtherWorkExperience}

\href{http://www.example.com/my-company}
{\textbf{CS 2110 Consultant}},
Cornell University
\hfill
\DatestampYMD{2016}{02}{09} --
Present

\GapNoBreak%
\BulletItem%
Responsible for helping other students be successful in CS 2110.

%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\section%
{Skills}
{Skills}
{PDF:Skills}

\BulletItem%
Java: Standard Libraries
\BulletItem%
OCaml: Standard Libraries, OCaml Core (Janestreet)
\BulletItem%
Vim
\BulletItem%
Commandline: Zsh, Bash, GNU Coreutils
\BulletItem%
Linux
\BulletItem%
Swift: Foundation, UIKit
\BulletItem%
{\LaTeX}
\BulletItem%
Perl
\BulletItem%
C++
\BulletItem%
C

%%%%%%%%%%%%%%%
%% LANGUAGES %%
%%%%%%%%%%%%%%%

\section%
{Languages}
{Languages}
{PDF:Languages}

\BulletItem%
English: Native language.

\GapNoBreak%
\BulletItem%
German: Advanced (speaking, reading, writing).
\begin{detail}
\SubBulletItem%
Raised speaking German at home.
\end{detail}

\GapNoBreak%
\BulletItem%
Spanish: Intermediate (reading, reading, writing).

%%%%%%%%%%%%%%%
%% INTERESTS %%
%%%%%%%%%%%%%%%

\section%
{Interests}
{Interests}
{PDF:Interests}

Board games,
Outdoors,
Hearthstone,
Running.

\end{body}

%\begin{flushright}
%\UseNoteFont%
%[\textit{\CVNote}]%
%\hspace{2.0mm}\null
%\end{flushright}

\label{LastPage}~%
\end{document}
